### 2020-07-29 draft.Rmd
FIx typos and clean up narrative

[@Ashraf2006] implemented a randomized control trial (RCT) to 1. see if individuals offered accounts opens accounts, and if so, what characteristics are associated with opening an account and 2. if individuals save more as a result of opening an account.

The authors partnered with a rural bank in Mindanao, Philippines called Green Bank of Caraga. After two rounds of randomization, they ended up with a survey size of 1,777 people who completed a baseline household survey. They then randomly assigned the individuals to the commitment treatment (T), marketing-treatment (M), and control (C) groups. One concern is that the commitment-savings may have a treatment effect because of the outreach or positive messaging around savings. The marketing treatment (M), a special visit to encourage savings using existing savings products only, was included to evaluate this effect. The marketing-treatment can also be thought of as a control. No pre-treatment observable differences between the three groups were statistically significantly different.

@@

We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial. We conclude using Tukey Permutation Honest Significant Difference tests that SEED accounts had more savings than the other two groups. Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].

@@

The right skew is present in the treatment and control groups, but it most pronounced in the commit-savings treatment group after twelve months as demonstrated in \textit{figure 3}.

@@

As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternate hypothesis. We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial. It is worth noting that we have not yet shown that the SEED accounts are more effective savings accounts than other methods, just that customers were able to save with them.

@@

In addition to testing whether or not the SEED accounts are more effective savings than a control group, we also want to confirm that the SEED accounts are more effective than just the marketing that comes with them. To do this we divide the customers into three groups. A control group, a group that receives marketing but not SEED accounts, and the group with SEED accounts.

@@

We are clearly comfortable with the first two assumptions. We are comfortable with the third assumption, because outliers aside, the we can see in Figure 4 that three treatments have similar spreads after the significant outliers are removed.

@@

A p-value of `r fp_result$p.val` for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate. We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.

@@

The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months as demonstrated in \textit{figure 2}. Accordingly, the dependent variable is not approximately normally distributed and the error term of their estimated models is not approximately normally distributed.

@@

[@Ashraf2006] estimate their models on the untransformed data and find only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS). Furthermore, they found that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.

@@

@@

In most cases our findings are aligned with the original paper. In section 3 we conclude that the SEED accounts are effective savings mechanisms, agreeing with the original authors. In section 4 we conclude that there is a difference between the three different treatments, but make a note that depending on the significance level employed we have reason to doubt that there is a difference between the marketing treatment and the SEED accounts. The tests concluded a difference, but further study is warranted. In section 5 we used different regression techniques from the original paper, as the authors had done a good bit of massaging to make OLS work. While the non parametric methods did conclude statistical siginificance of the SEED treatments over the marketing treatments, the coefficients determined by the methods were significantly lower. Leading us to conclude that while there is a statistically significant effect of the SEED accounts on savings compared to the marketing treatment, there is not necessarily a practically significant effect.

Overall, we conclude that the SEED accounts are effective saving mechanisms, with some marginal benefits over marketing treatments. However, like the authors of the original paper, we also recommend further study into the true effectiveness of the accounts, and how large the difference is between them and other potential marketing strategies.

>>>>

[@Ashraf2006] implemented a randomized control trial (RCT) to 1. see if individuals offered accounts open accounts, and if so, what characteristics are associated with opening an account and 2. if individuals save more as a result of opening an account.

The authors partnered with a rural bank in Mindanao, Philippines called Green Bank of Caraga. After two rounds of randomization, they ended up with a sample size of 1,777 people who completed a baseline household survey. They then randomly assigned the individuals to the commitment treatment (T), marketing-treatment (M), and control (C) groups. One concern is that the commitment-savings may have a treatment effect because of the outreach or positive messaging around savings. The marketing treatment (M), a special visit to encourage savings using existing savings products only, was included to evaluate this effect. The marketing-treatment can also be thought of as a control. No pre-treatment observable differences between the three groups were statistically significantly different.

@@

We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial. We conclude using Kruskal-Wallis tests that SEED accounts had more savings than the other two groups. Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].

@@

The right skew is present in the treatment and control groups, but is most pronounced in the commitment-savings treatment group after twelve months as demonstrated in \textit{figure 3}.

@@

As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternative hypothesis. We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial. It is worth noting that we have not yet shown that the SEED accounts are more effective savings accounts than other methods, just that customers were able to save with them.

@@

In addition to testing whether or not the SEED accounts are more effective for savings than a control group, we also want to test that the SEED accounts are more effective than just the marketing that comes with them. To do this we divide the customers into three groups. A control group, a group that receives marketing but not SEED accounts, and the group with SEED accounts.

@@

We are clearly comfortable with the first two assumptions. We are comfortable with the third assumption, because outliers aside, we can see in \textit{Figure 4} that three treatments have similar spreads after the significant outliers are removed.

@@

A p-value of `r fp_result$p.val` for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternative. We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.

@@

The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months as demonstrated in \textit{figure 2}. Accordingly, the dependent variable is not approximately normally distributed and the error terms of their estimated models are not approximately normally distributed.

@@

[@Ashraf2006] estimate their models on the untransformed data and find only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS). Furthermore, they find that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.

@@

All results in this section are in Philippine Pesos. About 50 Philippine Pesos converted to one U.S. Dollar when the data were collected.

@@

In most cases, the conclusions of our tests aligned with the original paper. In section 3 we conclude that the SEED accounts are effective savings mechanisms, agreeing with the original authors. In section 4 we conclude that there is a difference between the three different treatments, but make a note that depending on the significance level employed we have reason to doubt that there is a difference between the marketing treatment and the SEED accounts. The tests concluded a difference, but further study is warranted. In section 5 we used different regression techniques from the original paper, as the authors had done a good bit of massaging to make OLS work. While the nonparametric methods did conclude statistical significance of the SEED treatments over the marketing treatments, the coefficients determined by the methods were significantly lower. Leading us to conclude that while there is a statistically significant effect of the SEED accounts on savings compared to the marketing treatment, there is not necessarily a practically significant effect.

Overall, we conclude that the SEED accounts are modestly effective saving mechanisms, with some marginal benefits over marketing treatments. However, like the authors of the original paper, we also recommend further study into the true effectiveness of the accounts, and how large the difference is between them and other potential marketing strategies.
